Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-01-22 cordillera-cycle.tex
Rev. Jarosch: clarify where geoflux is applied.

      Basal topography is bilinearly interpolated from the ETOPO1 combined
      topography and bathymetry dataset with a~resolution of 1\,arc-min
      \citep{Amante.Eakins.2009} to the model grids. Sea level is lowered as
      a~function of time based on the Spectral Mapping Project
      \citep[SPECMAP,][]{Imbrie.etal.1989} time scale. Geothermal heat flux
      is applied as a~constant value of
      $q_{\mathrm{G}}=70$\,\unit{mW\,m^{-2}} at
      3\,\unit{km} depth (Sect.~\ref{sec:icedyn}). Basal sliding follows
      a pseudo-plastic law where the yield stress accounts for till
      deconsolidation under high water pressure (Sect.~\ref{sec:sliding}).
      Ice shelf calving is calculated based on ice thickness and principle
      strain rates (Sect.~\ref{sec:sliding}). Surface mass balance is
      computed using a~positive degree-day (PDD) model
      (Sect.~\ref{sec:surface}). Default parameter values are given in
      Table~\ref{tab:params}. Climate forcing is provided by a~monthly
      climatology averaged from 1979 to 2000 from the North American
      Regional Reanalysis \citep[NARR,][]{Mesinger.etal.2006}, perturbated
      by time-dependent offsets and lapse-rate temperature corrections
      (Sect.~\ref{sec:atm}, Table~\ref{tab:records}). A sensitivity study
      to some of the most influential ice rheology (Sect~\ref{sec:icedyn})
      and basal sliding (Sect.~\ref{sec:sliding}) parameters was performed
      (Table~\ref{tab:sens_params}).

@@

      Surface air
      temperature derived from the climate forcing (Sect.~\ref{sec:atm})
      provides the upper boundary condition to the ice enthalpy
      model. Temperature is computed subglacially to a~depth of
      3\,\unit{km}, where it is conditioned by a~lower boundary geothermal
      heat flux of 70\,\unit{mW\,m^{-2}}. Although this uniform value does
      not account for the high spatial geothermal variability in the region
      \citep{Blackwell.Richards.2004}, it is, on average, representative of
      available heat flow measurements. In the low-resolution simulations,
      the vertical grid consists of 31~temperature layers in the bedrock and
      up to 51~enthalpy layers in the ice sheet, corresponding to a~vertical
      resolution of 100\,\unit{m}. The high-resolution simulations
      61~bedrock layers and up to 101~ice layers with a~vertical resolution
      of 50\,\unit{m}.

>>>>

      Basal topography is bilinearly interpolated from the ETOPO1 combined
      topography and bathymetry dataset with a~resolution of 1\,arc-min
      \citep{Amante.Eakins.2009} to the model grids. Sea level is lowered as
      a~function of time based on the Spectral Mapping Project
      \citep[SPECMAP,][]{Imbrie.etal.1989} time scale. Ice deformation
      follows temperature and water-content dependent creep
      (Sect.~\ref{sec:icedyn}). Basal sliding follows
      a pseudo-plastic law where the yield stress accounts for till
      deconsolidation under high water pressure (Sect.~\ref{sec:sliding}).
      Ice shelf calving is calculated based on ice thickness and principle
      strain rates (Sect.~\ref{sec:sliding}). Surface mass balance is
      computed using a~positive degree-day (PDD) model
      (Sect.~\ref{sec:surface}). Default parameter values are given in
      Table~\ref{tab:params}. Climate forcing is provided by a~monthly
      climatology averaged from 1979 to 2000 from the North American
      Regional Reanalysis \citep[NARR,][]{Mesinger.etal.2006}, perturbated
      by time-dependent offsets and lapse-rate temperature corrections
      (Sect.~\ref{sec:atm}, Table~\ref{tab:records}). A sensitivity study
      to some of the most influential ice rheology (Sect~\ref{sec:icedyn})
      and basal sliding (Sect.~\ref{sec:sliding}) parameters was performed
      (Table~\ref{tab:sens_params}).

@@

      Surface air
      temperature derived from the climate forcing (Sect.~\ref{sec:atm})
      provides the upper boundary condition to the ice enthalpy
      model. Temperature is computed in the ice and in the bedrock to
      a~depth of 3\,\unit{km} below the ice-bedrock interface, where it is
      conditioned by a~lower boundary geothermal heat flux of
      $q_{\mathrm{G}}=70$\,\unit{mW\,m^{-2}}. Although this uniform value
      does
      not account for the high spatial geothermal variability in the region
      \citep{Blackwell.Richards.2004}, it is, on average, representative of
      available heat flow measurements. In the low-resolution simulations,
      the vertical grid consists of 31~temperature layers in the bedrock and
      up to 51~enthalpy layers in the ice sheet, corresponding to a~vertical
      resolution of 100\,\unit{m}. The high-resolution simulations
      61~bedrock layers and up to 101~ice layers with a~vertical resolution
      of 50\,\unit{m}.
